The Heavy Photon Search Test Detector

### 2014-03-25 hps-testrun-nim.tex
Added MCS references.

\subsection{Trigger Rate Comparisons}
\label{sec:mcs}
Trigger rates observed in the Test run are dominated by multiple scattered pair-produced \ee pairs in the 
converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular distribution 
and the sub-sequent multiple Coulomb scattering in the converter. Rates from different converter 
thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
angle is constant). Restricting clusters to a well calibrated region of the ECal and subtracting the 
"no converter" background we see agreement with the rates predicted by the \egs{} simulation 
program, see Tab.~\ref{tab:mcs}.
%\begin{center}
\begin{table}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\label{tab:mcs}
\end{table}
%\end{center}
This gives further confidence that the dominant source of background occupancy for HPS, multiple Coulomb 
scattered beam electrons, is well described. 
%One of the main goals of the Test run was to evaluate the description of the tails of the 
%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
%Despite all data taken with a photon beam in the Test run,

>>>>

\subsection{Trigger Rate Comparisons}
\label{sec:mcs}
Trigger rates observed in the Test run are dominated by multiple scattered pair-produced \ee pairs in the 
converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular distribution 
and the sub-sequent multiple Coulomb scattering in the converter. Rates from different converter 
thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
angle is constant). Restricting clusters to a well calibrated region of the ECal and subtracting the 
"no converter" background we see agreement with the rates predicted by the \egs{} simulation 
program, see Tab.~\ref{tab:mcs}.
%\begin{center}
\begin{table}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted number of events for 1~s of beam at 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\label{tab:mcs}
\end{table}
%\end{center}
This gives further confidence that the dominant source of background occupancy for HPS, multiple 
Coulomb scattered beam electrons, is well 
described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
%One of the main goals of the Test run was to evaluate the description of the tails of the 
%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
%Despite all data taken with a photon beam in the Test run,
